On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-11-22 paper.tex
update 11/22 in tokyo

%//////////////////////////////////////////////////////%
%//////////////////////////////////////////////////////%
%Kohei
%//////////////////////////////////////////////////////%
%//////////////////////////////////////////////////////%

@@

      \draw[dashed] (0,0)--(1.5,0);
      \draw[dashed] (1.5,0)--(3,0);
      \draw[dashed] (3,0)--(4.5,0);
      \draw[dashed] (4.5,0)--(6,0);
      \draw[->] (0,0)--(60:1.3);
      \draw[->] (1.5,0)--++(60:1.3);
      \draw[->] (3,0)--++(60:1.3);
      \draw[->] (4.5,0)--++(60:1.3);

      \begin{scope}[shift=(60:1.5)]
        \fill (0,0) circle[radius = 0.1];
        \fill (1.5,0) circle[radius = 0.1];
        \fill (3,0) circle[radius = 0.1];
        \fill (4.5,0) circle[radius = 0.1];
        \draw[dashed] (0,0)--(1.5,0);
        \draw[dashed] (1.5,0)--(3,0);
        \draw[dashed] (3,0)--(4.5,0);
        \draw[->] (0,0)--(-60:1.3);
        \draw[->] (1.5,0)--++(-60:1.3);
        \draw[->] (3,0)--++(-60:1.3);
        \draw[->] (4.5,0)--++(-60:1.3);
      \end{scope}

@@

\begin{figure}
  \begin{center}
    \begin{tikzpicture}
      \fill (0:0) circle [radius=0.05];
      \fill (0:1.2) circle [radius=0.05];
      \fill (180:1.2) circle [radius=0.05];
      \node[above] at (0:1.2) { $p^\prime$ };
      \node[above] at (0:0) { $p$ };
      \node[above] at (180:1.2) { $p^\prime$ };

      \fill (60 : 1.2) circle [radius=0.1];
      \fill (-60 : 1.2) circle [radius=0.1];
      \fill (120 : 1.2) circle [radius=0.1];
      \fill (-120 : 1.2) circle [radius=0.1];
      \node[above] at (60 :1.2) { $a_{j_1}$ };
      \node[above] at (-60 :1.2) { $a_{j_2}$ };
      \node[above] at (120 :1.2) { $a_{j_3}$ };
      \node[above] at (-120 :1.2) { $a_{j_4}$ };

      \begin{scope}[shift=(0:5)]
        \fill (0:0) circle [radius=0.1];
        \fill (0:1.2) circle [radius=0.05];
        \fill (180:1.2) circle [radius=0.1];
        \node[above] at (180:1.2) { $a_{i-2}$ };
        \node[above] at (0:0) { $a_{i-1}$ };
        \draw[->] (180:1.1) -- (180:0.1);

        \fill (60 : 1.2) circle [radius=0.1];
        \fill (-60 : 1.2) circle [radius=0.1];
        \fill (120 : 1.2) circle [radius=0.1];
        \fill (-120 : 1.2) circle [radius=0.1];
        \node[above] at (60 :1.2) { $a_{j_1}$ };
        \node[above] at (-60 :1.2) { $a_{j_2}$ };
        \node[above] at (120 :1.2) { $a_{j_3}$ };
        \node[above] at (-120 :1.2) { $a_{j_4}$ };
      \end{scope}
      \begin{scope}[shift=(0:10)]
        \fill (0:0) circle [radius=0.1];
        \fill (0:1.2) circle [radius=0.1];
        \fill (180:1.2) circle [radius=0.1];
        \node[above] at (180:1.2) { $a_{i-2}$ };
        \node[above] at (0:0) { $a_{i-1}$ };
        \node[above] at (0:1.2) { $a_i$ };
        \draw[->] (180:1.1) -- (180:0.1);
        \draw[->] (0:0.1) -- (0:1.1);

        \fill (60 : 1.2) circle [radius=0.1];
        \fill (-60 : 1.2) circle [radius=0.1];
        \fill (120 : 1.2) circle [radius=0.1];
        \fill (-120 : 1.2) circle [radius=0.1];
        \node[above] at (60 :1.2) { $a_{j_1}$ };
        \node[above] at (-60 :1.2) { $a_{j_2}$ };
        \node[above] at (120 :1.2) { $a_{j_3}$ };
        \node[above] at (-120 :1.2) { $a_{j_4}$ };
      \end{scope}
    \end{tikzpicture} 
    \caption{Through a tunnel section}
    \label{TTT_tunnel_intro}
  \end{center}
\end{figure}

@@

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}
          \begin{scope}[xshift=2cm, yshift=2cm]
            \fill(0,0) circle [radius=0.05];
            \node[above] at (180:1.2) {$p^\prime$};
            \node[above] at (0:1.2) {$p^\prime$};

            \foreach \theta in {0,180}{
              \fill[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.05];
            }

            \foreach \theta in {60,-60,120,-120}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
            }
          \end{scope}

@@

          \begin{scope}[xshift=2cm, yshift=2cm]
            \fill(0,0) circle [radius=0.05];
            \node[above] at (180:1.2) {$p^\prime$};
            \node[above] at (-60:1.2) {$p^\prime$};

            \foreach \theta in {-60,180}{
              \fill[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.05];
            }

            \foreach \theta in {0,60,120,-120}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
            }
          \end{scope}

@@

          \begin{scope}[xshift=2cm, yshift=2cm]
            \fill(0,0) circle [radius=0.05];
            \node[above] at (180:1.2) {$p^\prime$};
            \node[above] at (-1200:1.2) {$p^\prime$};

            \foreach \theta in {-120,180}{
              \fill[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.05];
            }

            \foreach \theta in {0,60,-60,120}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
            }
          \end{scope}

@@

      \begin{minipage}{0.3\hsize}
      \centering
        \begin{tikzpicture}
	 \draw[->,white] (120:1.1)--(120:0.1);%for adjustment

            \fill(0,0) circle [radius=0.1];
            \node[below] at (0,0) {$p^\prime$};

            \foreach \theta in {0}{
              \draw[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.1];
            }

            \foreach \theta in {60,-60,180}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
            }

            \foreach \theta in {120,-120}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
            }

            \draw[->] (180:1.1)--(180:0.1);
            \draw[->] (0:0.1)--(0:1.1);

            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};

@@

            \fill(0,0) circle [radius=0.1];
            \node[below] at (0,0) {$p^\prime$};

            \foreach \theta in {0}{
              \draw[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.1];
            }

            \foreach \theta in {60,-60,120}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
            }

            \foreach \theta in {180,-120}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
            }

            \draw[->] (120:1.1)--(120:0.1);
            \draw[->] (0:0.1)--(0:1.1);

            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};
            \node[transform canvas={shift=(180:1.2)},left] {$n_5$};

@@

      \begin{minipage}{0.3\hsize}
      \centering
        \begin{tikzpicture}
            \fill(0,0) circle [radius=0.1];
            \node[above] at (0,0) {$p^\prime$};

            \foreach \theta in {0}{
              \draw[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.1];
            }

            \foreach \theta in {60,-60}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
            }

            \foreach \theta in {180,-120,120}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
            }

            \draw[->] (60:1.1)--(60:0.1);
            \draw[->] (0:0.1)--(0:1.1);

            \node[transform canvas={shift=(0:1.2)},below] {$n_0$};
            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};
            \node[transform canvas={shift=(180:1.2)},left] {$n_5$};

@@

Fig.\ref{TTT_tunnel_exit} exhibits all the two kings of exit of tunnel. 
At least one of point $n_1$ or $n_2$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.

@@

            \fill(0,0) circle [radius=0.1];
            \node[above] at (0,0) {$p^\prime$};

            \foreach \theta in {120,-120,180}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
            }

            \foreach \theta in {0,60,-60}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
            }

            \draw[->] (180:1.1)--(180:0.1);

            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};
            \node[transform canvas={shift=(180:1.2)},left] {$n_5$};

@@

            \fill(0,0) circle [radius=0.1];
            \node[above] at (0,0) {$p^\prime$};

            \foreach \theta in {120,-120,180,60}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
            }

            \foreach \theta in {0,-60}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
            }

            \draw[->] (180:1.1)--(180:0.1);

            \node[transform canvas={shift=(0:1.2)},right] {$n_0$};
            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};
            \node[transform canvas={shift=(180:1.2)},left] {$n_5$};

@@

          \draw[transform canvas={shift=(0:0)}](-0.1,-0.1)--(0.1,0.1);
          \draw[transform canvas={shift=(0:0)}](0.1,-0.1)--(-0.1,0.1);

          \foreach \theta in {60,-60,120,-120,180}{
            \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
            \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
          }

          \fill(0:1.2) circle [radius=0.1];
          \draw[->] (0:0.1)--(0:1.1);

          \node[left] at (-60:1.2) {$n_4$};

          \begin{scope}[shift=(0:2.4)]
            \fill(0,0) circle [radius=0.1];

            \foreach \theta in {120,60,-60,0}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
            }

            \draw[->] (180:1.1)--(180:0.1);
            \draw[->] (-120:0.1)--(-120:1.1);

            \node[below] at (180:1.2) {$w[i-2]$};
            \node[above] at (0:0) {$w[i-1]$};
            \node[right] at (-120:1.2) {$w[i]$};

            \node[left] at (120:1.2) {$n_3$};
            \node[left] at (60:1.2) {$n_2$};
            \node[left] at (0:1.2) {$n_1$};

            \begin{scope}[shift=(-120:1.2)]
              \draw(0,0) circle [radius=0.1];
              \foreach \theta in {-120,-60}{
                \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
              }

              \node[right] at (-120:1.2) {$n_5$};
              \node[right] at (-60:1.2) {$n_6$};
            \end{scope}

@@

          \draw[transform canvas={shift=(0:0)}](-0.1,-0.1)--(0.1,0.1);
          \draw[transform canvas={shift=(0:0)}](0.1,-0.1)--(-0.1,0.1);

          \foreach \theta in {60,0,120,-120,180}{
            \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
            \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
          }

          \draw[->] (-60:0.1)--(-60:1.1);

          \begin{scope}[shift=(-60:1.2),shift=(0:1.2)]
            \fill(0,0) circle [radius=0.1];
            \fill(180:1.2) circle [radius=0.1];

            \foreach \theta in {120,60,0,-60}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
            }

            \draw[->] (180:1.1)--(180:0.1);
            \draw[->] (-120:0.1)--(-120:1.1);

            \node[below] at (180:1.2) {$w[i-2]$};
            \node[above] at (0:0) {$w[i-1]$};
            \node[right] at (-120:1.2) {$w[i]$};

            \node[left] at (120:1.2) {$n_3$};
            \node[left] at (60:1.2) {$n_2$};
            \node[left] at (0:1.2) {$n_1$};

            \begin{scope}[shift=(-120:1.2)]
              \draw(0,0) circle [radius=0.1];
              \foreach \theta in {180,-120,-60}{
                \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
              }

              \node[right] at (180:1.2) {$n_4$};
              \node[right] at (-120:1.2) {$n_5$};
              \node[right] at (-60:1.2) {$n_6$};
            \end{scope}

@@

\begin{figure}
  \begin{center}
        \begin{tikzpicture}
        \draw[->,white] (-70:0.1) -- (-70:3);
          \foreach \theta in {60,-60,120,0}{
            \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
            \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
          }

          \fill(180:1.2) circle [radius=0.1];
          \fill(0:0) circle [radius=0.1];

          \draw[transform canvas={shift=(180:1.2)}] (105:1.1) edge[bend right] (105:0.1);
          \draw[->] (180:1.1) -- (180:0.1);
          \draw[->] (-120:0.1) -- (-120:1.1);

          \node[below] at (180:1.2) {$w[i-2]$};
          \node[above] at (0:0) {$w[i-1]$};
          \node[left] at (-120:1.2) {$w[i]$};

          \node[right] at (120:1.2) {$n_3$};
          \node[right] at (60:1.2) {$n_2$};
          \node[right] at (0:1.2) {$n_1$};

          \begin{scope}[shift=(-120:1.2)]
            \draw(0,0) circle [radius=0.1];
            \foreach \theta in {-120,-60,180}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
            }

@@

Let us consider the case of $v_k$ is $o$. See Fig.\ref{TTT_case_of_o}. $w[i-1]$ consumes some binding capabilities because $v_{i-1}$ is $b$. If the number of $w[i-1]$'s bindings is one binding, then $w[i+1]$ has to be bound except $n_1$ or $n_2$ so that $w[i+1]$ must consumes two bindings except the case of $n_1$ and $n_2$ are occupied and $w[i]$ consumes at least one binding. If $n_1$ and $n_2$ are occupied, then $w[i-1]$'s binginds are inactive that is $w[i-1]$ consumes two binding capabilities. Therefore, this case consumes binding capabilities. If $w[i-1]$ dose Not have any bindings, then $w[i-1]$ already consumes two bindings. In addition, $w[i]$ and $w[i+1]$ consume at least one binding. Therefore this case consumes binding capabilities. Thus, the formula \ref{TTT_only_a} hold and according to the formula \ref{TTT_only_bond} and the formula \ref{TTT_only_a}, the formula \ref{TTT_structure} is hold.

@@

      \draw[transform canvas={shift=(-120:1.2)}](-0.1,-0.1)--(0.1,0.1);
      \draw[transform canvas={shift=(-120:1.2)}](0.1,-0.1)--(-0.1,0.1);

>>>>

%//////////////////////////////////////////////////////%
%//////////////////////////////////////////////////////%
%Kohei
%//////////////////////////////////////////////////////%
%//////////////////////////////////////////////////////%l.168 - 1324

@@

      \draw[dashed] (0,0)--(1.5,0);
      \draw[dashed] (1.5,0)--(3,0);
      \draw[dashed] (3,0)--(4.5,0);
      \draw[dashed] (4.5,0)--(6,0);
      \draw[->] (0,0)--(60:0.75);
      \draw[->] (1.5,0)--++(60:0.75);
      \draw[->] (3,0)--++(60:0.75);
      \draw[->] (4.5,0)--++(60:0.75);
      \draw (0,0)--(60:1.5);
      \draw (1.5,0)--++(60:1.5);
      \draw (3,0)--++(60:1.5);
      \draw (4.5,0)--++(60:1.5);

      \begin{scope}[shift=(60:1.5)]
        \fill (0,0) circle[radius = 0.1];
        \fill (1.5,0) circle[radius = 0.1];
        \fill (3,0) circle[radius = 0.1];
        \fill (4.5,0) circle[radius = 0.1];
        \draw[dashed] (0,0)--(1.5,0);
        \draw[dashed] (1.5,0)--(3,0);
        \draw[dashed] (3,0)--(4.5,0);
        \draw[->] (0,0)--(-60:0.75);
        \draw[->] (1.5,0)--++(-60:0.75);
        \draw[->] (3,0)--++(-60:0.75);
        \draw[->] (4.5,0)--++(-60:0.75);

        \draw (0,0)--(-60:1.5);
        \draw (1.5,0)--++(-60:1.5);
        \draw (3,0)--++(-60:1.5);
        \draw (4.5,0)--++(-60:1.5);
      \end{scope}

@@

\begin{figure}
  \begin{center}
    \begin{tikzpicture}
      \draw (0:0) circle [radius=0.05];
      \draw (0:1) circle [radius=0.05];
      \draw (180:1) circle [radius=0.05];
      \node[above] at (0:1) { $p^\prime$ };
      \node[above] at (0:0) { $p$ };
      \node[above] at (180:1) { $p^\prime$ };

      \fill (60 : 1) circle [radius=0.1];
      \fill (-60 : 1) circle [radius=0.1];
      \fill (120 : 1) circle [radius=0.1];
      \fill (-120 : 1) circle [radius=0.1];
      \node[above] at (60 :1) { $a_{j_1}$ };
      \node[above] at (-60 :1) { $a_{j_2}$ };
      \node[above] at (120 :1) { $a_{j_3}$ };
      \node[above] at (-120 :1) { $a_{j_4}$ };

      \begin{scope}[shift=(0:5)]
        \fill[blue] (0:0) circle [radius=0.1];
        \draw (0:1) circle [radius=0.05];
        \fill (180:1) circle [radius=0.1];
        \node[above] at (180:1.2) { $a_{i-2}$ };
        \node[above] at (0:0) { $a_{i-1}$ };
        \draw[->, blue] (180:0.9) -- (180:0.1);

        \fill (60 : 1) circle [radius=0.1];
        \fill (-60 : 1) circle [radius=0.1];
        \fill (120 : 1) circle [radius=0.1];
        \fill (-120 : 1) circle [radius=0.1];
        \node[above] at (60 :1) { $a_{j_1}$ };
        \node[above] at (-60 :1) { $a_{j_2}$ };
        \node[above] at (120 :1) { $a_{j_3}$ };
        \node[above] at (-120 :1) { $a_{j_4}$ };
      \end{scope}
      \begin{scope}[shift=(0:10)]
        \fill (0:0) circle [radius=0.1];
        \fill[blue] (0:1) circle [radius=0.1];
        \fill (180:1) circle [radius=0.1];
        \node[above] at (180:1) { $a_{i-2}$ };
        \node[above] at (0:0) { $a_{i-1}$ };
        \node[above] at (0:1) { $a_i$ };
        \draw[->] (180:0.9) -- (180:0.1);
        \draw[->,blue] (0:0.1) -- (0:0.9);

        \fill (60 : 1) circle [radius=0.1];
        \fill (-60 : 1) circle [radius=0.1];
        \fill (120 : 1) circle [radius=0.1];
        \fill (-120 : 1) circle [radius=0.1];
        \node[above] at (60 :1) { $a_{j_1}$ };
        \node[above] at (-60 :1) { $a_{j_2}$ };
        \node[above] at (120 :1) { $a_{j_3}$ };
        \node[above] at (-120 :1) { $a_{j_4}$ };
      \end{scope}
    \end{tikzpicture} 
    \caption{Through a tunnel section}
    \label{TTT_tunnel_intro}
  \end{center}
\end{figure}

@@

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}
          \begin{scope}[xshift=2cm, yshift=2cm]
            \draw(0,0) circle [radius=0.05];
            \node[above] at (180:1) {$p^\prime$};
            \node[above] at (0:1) {$p^\prime$};

            \foreach \theta in {0,180}{
              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
            }

            \foreach \theta in {60,-60,120,-120}{
              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
            }
          \end{scope}

@@

          \begin{scope}[xshift=2cm, yshift=2cm]
            \draw(0,0) circle [radius=0.05];
            \node[above] at (180:1) {$p^\prime$};
            \node[above] at (-60:1) {$p^\prime$};

            \foreach \theta in {-60,180}{
              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
            }

            \foreach \theta in {0,60,120,-120}{
 	            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
            }
          \end{scope}

@@

          \begin{scope}[xshift=2cm, yshift=2cm]
            \draw(0,0) circle [radius=0.05];
            \node[above] at (180:1) {$p^\prime$};
            \node[above] at (-1200:1) {$p^\prime$};

            \foreach \theta in {-120,180}{
              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
            }

            \foreach \theta in {0,60,-60,120}{
              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
            }
          \end{scope}

@@

      \begin{minipage}{0.3\hsize}
      \centering
        \begin{tikzpicture}
	 \draw[->,white] (120:0.8)--(120:0.1);%for adjustment

            \fill[blue] (0,0) circle [radius=0.05];
            \node[below] at (0,0) {$p^\prime$};

            \foreach \theta in {0}{
              \fill[transform canvas={shift=(\theta:1)},blue](0,0) circle [radius=0.05];
            }

            \foreach \theta in {60,-60,180}{
              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
            }

            \foreach \theta in {120,-120}{
              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
            }

            \draw[->, blue] (180:0.9)--(180:0.1);
            \draw[->, blue] (0:0.1)--(0:0.9);

            \node[transform canvas={shift=(60:1)},right] {$n_1$};
            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
            \node[transform canvas={shift=(120:1)},left] {$n_3$};
            \node[transform canvas={shift=(-120:1)},left] {$n_4$};

@@

            \fill(0,0) circle [radius=0.05];
            \node[below] at (0,0) {$p^\prime$};

            \foreach \theta in {0}{
              \fill[transform canvas={shift=(\theta:1)},blue](0,0) circle [radius=0.05];
            }

            \foreach \theta in {60,-60,120}{
              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
            }

            \foreach \theta in {180,-120}{
              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
            }

            \draw[->, blue] (120:0.9)--(120:0.1);
            \draw[->, blue] (0:0.1)--(0:0.9);

            \node[transform canvas={shift=(60:1)},right] {$n_1$};
            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
            \node[transform canvas={shift=(120:1)},left] {$n_3$};
            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
            \node[transform canvas={shift=(180:1)},left] {$n_5$};

@@

      \begin{minipage}{0.3\hsize}
      \centering
        \begin{tikzpicture}
            \fill[blue](0,0) circle [radius=0.05];
            \node[above] at (0,0) {$p^\prime$};

            \foreach \theta in {0}{
              \fill[transform canvas={shift=(\theta:1)}, blue](0,0) circle [radius=0.05];
            }

            \foreach \theta in {60,-60}{
              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
            }

            \foreach \theta in {180,-120,120}{
              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
            }

            \draw[->, blue] (60:1.1)--(60:0.1);
            \draw[->, blue] (0:0.1)--(0:1.1);

            \node[transform canvas={shift=(0:1)},below] {$n_0$};
            \node[transform canvas={shift=(60:1)},right] {$n_1$};
            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
            \node[transform canvas={shift=(120:1)},left] {$n_3$};
            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
            \node[transform canvas={shift=(180:1)},left] {$n_5$};

@@

Fig.\ref{TTT_tunnel_exit} exhibits all the two kinds of exit of tunnel. 
At least one of point $n_1$ or $n_2$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.

@@

            \fill[blue](0,0) circle [radius=0.05];
            \node[above] at (0,0) {$p^\prime$};

            \foreach \theta in {120,-120,180}{
              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
            }

            \foreach \theta in {0}{
              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
            }
            \draw (-60:1) circle [radius=0.05];
            \draw (60:1) circle [radius=0.05];

            \draw[->, blue] (180:0.9)--(180:0.1);

            \node[transform canvas={shift=(60:1)},right] {$n_1$};
            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
            \node[transform canvas={shift=(120:1)},left] {$n_3$};
            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
            \node[transform canvas={shift=(180:1)},left] {$n_5$};

@@

            \fill[blue](0,0) circle [radius=0.05];
            \node[above] at (0,0) {$p^\prime$};

            \foreach \theta in {120,-120,180,60}{
              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
            }

            \foreach \theta in {0}{
              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
            }
            \draw (-60:1) circle [radius=0.05];

            \draw[->, blue] (180:0.9)--(180:0.1);

            \node[transform canvas={shift=(0:1)},right] {$n_0$};
            \node[transform canvas={shift=(60:1)},right] {$n_1$};
            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
            \node[transform canvas={shift=(120:1)},left] {$n_3$};
            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
            \node[transform canvas={shift=(180:1)},left] {$n_5$};

@@

          \fill[transform canvas={shift=(0:0)}](0,0) circle [radius=0.1];

          \foreach \theta in {60,-60,120,-120,180}{
            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
          }

          \fill[blue](0:1) circle [radius=0.05];
          \draw[->, blue] (0:0.1)--(0:0.9);

          \node[below] at (-60:1) {$n_4$};

          \begin{scope}[shift=(0:2)]
            \fill[blue](0,0) circle [radius=0.05];

            \foreach \theta in {120,60,-60,0}{
             \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
            }

            \draw[->, blue] (180:0.9)--(180:0.1);
            \draw[->, blue] (-120:0.1)--(-120:0.9);

            \node[below] at (180:1) {$w[i-2]$};
            \node[above] at (0:0) {$w[i-1]$};
            \node[right] at (-120:1) {$w[i]$};

            \node[above] at (120:1) {$n_3$};
            \node[above] at (60:1) {$n_2$};
            \node[right] at (0:1) {$n_1$};

            \begin{scope}[shift=(-120:1)]
              \fill[blue](0,0) circle [radius=0.05];
              \foreach \theta in {-120,-60}{
                \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
              }

              \node[right] at (-120:1) {$n_5$};
              \node[right] at (-60:1) {$n_6$};
            \end{scope}

@@

          \fill(0,0) circle [radius=0.1];

          \foreach \theta in {60,0,120,-120,180}{
            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
          }

          \draw[->, blue] (-60:0.1)--(-60:0.9);

          \begin{scope}[shift=(-60:1),shift=(0:1)]
            \fill[blue](0,0) circle [radius=0.05];
            \fill[blue](180:1) circle [radius=0.05];

            \foreach \theta in {120,60,0,-60}{
              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
            }

            \draw[->, blue] (180:0.9)--(180:0.1);
            \draw[->, blue] (-120:0.1)--(-120:0.9);

            \node[below] at (180:1) {$w[i-2]$};
            \node[above] at (0:0) {$w[i-1]$};
            \node[right] at (-120:1) {$w[i]$};

            \node[above right] at (120:1) {$n_3$};
            \node[right] at (60:1) {$n_2$};
            \node[right] at (0:1) {$n_1$};

            \begin{scope}[shift=(-120:1)]
              \fill(0,0) circle [radius=0.05];
              \foreach \theta in {180,-120,-60}{
                \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
              }

              \node[right] at (180:1) {$n_4$};
              \node[right] at (-120:1) {$n_5$};
              \node[right] at (-60:1) {$n_6$};
            \end{scope}

@@

\begin{figure}
  \begin{center}
        \begin{tikzpicture}
        \draw[->,white] (-70:0.1) -- (-70:3);
          \foreach \theta in {60,-60,120,0}{
            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
          }

          \fill[blue](180:1) circle [radius=0.05];
          \fill[blue](0:0) circle [radius=0.05];

          \draw[transform canvas={shift=(180:1)}, blue] (105:1) edge[bend right] (105:0);
          \draw[->, blue] (180:0.9) -- (180:0.1);
          \draw[->, blue] (-120:0.1) -- (-120:0.9);

          \node[below left] at (180:1) {$w[i-2]$};
          \node[above] at (0:0) {$w[i-1]$};
          \node[below] at (-120:1) {$w[i]$};

          \node[right] at (120:1) {$n_3$};
          \node[right] at (60:1) {$n_2$};
          \node[right] at (0:1) {$n_1$};

          \begin{scope}[shift=(-120:1)]
            \fill[blue](0,0) circle [radius=0.05];
            \foreach \theta in {-120,-60,180}{
              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
            }

@@

Let us consider the case of $v_k$ is $o$. See Fig.\ref{TTT_case_of_o}. $w[i-1]$ consumes some binding capabilities because $v_{i-1}$ is $b$. If the number of $w[i-1]$'s bindings is one binding, then $w[i+1]$ has to be bound except $n_1$ or $n_2$ so that $w[i+1]$ must consumes two bindings except the case of $n_1$ and $n_2$ are occupied and $w[i]$ consumes at least one binding. If $n_1$ and $n_2$ are occupied, then $w[i-1]$'s bindings are inactive that is $w[i-1]$ consumes two binding capabilities. Therefore, this case consumes binding capabilities. If $w[i-1]$ dose Not have any bindings, then $w[i-1]$ already consumes two bindings. In addition, $w[i]$ and $w[i+1]$ consume at least one binding. Therefore this case consumes binding capabilities. Thus, the formula \ref{TTT_only_a} hold and according to the formula \ref{TTT_only_bond} and the formula \ref{TTT_only_a}, the formula \ref{TTT_structure} is hold.

@@

      \fill[transform canvas={shift=(-120:1)}](0,0) circle [radius=0.1];

      \fill[blue](0:0) circle [radius=0.05];
      \fill[blue](0:1) circle [radius=0.05];
      \fill[shift=(0:1), blue](40:1) circle [radius=0.05];

      \draw[->, blue] (-120:1) edge[bend left] (-120:0.1);
      \draw[->, blue] (0:0.1) -- (0:0.9);
      \draw[->,transform canvas={shift=(0:1.2)}, blue] (50:0) -- (47:0.8);
